\documentclass[10pt]{beamer}

\usetheme[progressbar=frametitle]{metropolis}

\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\usepackage{minted}

\usepackage{pgfplots}

\usepackage{xspace}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}

\title{Futuristic Error Handling}
\subtitle{Error handling in C++ today and tomorrow}
\logo{test}
% \date{\today}
\date{}
\author{Dawid Pilarski}
\institute{dawid.pilarski@panicsofware.com}

\begin{document}

\maketitle

%\begin{frame}{Table of contents}
%  \setbeamertemplate{section in toc}[sections numbered]
%  \tableofcontents[hideallsubsections]
%\end{frame}

\section{Introduction}

\begin{frame}{Why am I here?}
	Why should we bother with error handling?

\end{frame}


\begin{frame}{Recommendable error handling mechanism}
	Which error mechanism would you choose?
	
	\begin{itemize}
		\item error codes?
		\item exceptions?
	\end{itemize}
\end{frame}

\section{Error codes nowadays}
\begin{frame}{The error codes.}
	\begin{itemize}[<+- | alert@+>]
		\item Old. C-compatible. Comes from assembly time.
		\item Machine friendly.
		\item Super fast.
		\item Used till today.
	\end{itemize}
\end{frame}

\begin{frame}[fragile]{Error code example}
	\begin{minted}{c++}
int sqlite3_open( const char *filename, sqlite3 **ppDb );
	\end{minted}
	
	\pause
	
	\hrulefill
	
	\begin{minted}{c++}
int open_status = sqlite3_open(/* ... */ );
if(open_status == SQLITE_OK){
  // make use of opened database
} else if( open_status == SQLITE_CANTOPEN_ISDIR ) {
  // handle the error
}
	\end{minted}
	
\end{frame}

\begin{frame}{Handle the error}
	How to handle the error correctly?
	
	\pause
	
	\begin{itemize}[<+- | alert@+>]
		\item \texttt{std::terminate()}
		\item take the error callback
		\item propagate the error to the caller
	\end{itemize}
	
\end{frame}



\section{Titleformats}

\begin{frame}{Metropolis titleformats}
\end{frame}


\appendix

\begin{frame}[fragile]{Backup slides}
  Sometimes, it is useful to add slides at the end of your presentation to
  refer to during audience questions.

  The best way to do this is to include the \verb|appendixnumberbeamer|
  package in your preamble and call \verb|\appendix| before your backup slides.

  \themename will automatically turn off slide numbering and progress bars for
  slides in the appendix.
\end{frame}

\begin{frame}[allowframebreaks]{References}

  \bibliography{demo}
  \bibliographystyle{abbrv}

\end{frame}

\end{document}
